Paper 1

### 2022-07-13 scripts/Paper 1.Rmd
add et plot

```{r VPD, echo=FALSE, message = FALSE, fig.width = 9, fig.height = 4}
(VPD.p <- ggplot(input.rearranged, aes(x = dayssinceJun1, y = VPD, group = GSYear)) +
  geom_line(aes(color = GSYear), size = 1)+
    scale_color_manual(values = group.colour) +
 # scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  xlab("Days since June 1st")+
   ylab("VPD (kPa")+
  theme_classic())+
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13),
          legend.text = element_text(size = 13),
          legend.title = element_text(size = 14))

VPD.p
tiff("VPD.tiff", units="in", width=10, height=6,  res=300)
print(VPD.p)
dev.off()

@@

```{r, echo=FALSE, message = FALSE, fig.width = 7, fig.height = 4}
group.colour <- c("19/20" = "#E69F00", "20/21" = "#009E73", "21/22" ="#D55E00")

@@

SWC.20
tiff("SWC20.tiff", units="in", width=10, height=6,  res=300)
print(SWC.20)
dev.off()
```

```{r add seasons, include=FALSE}
#rainfall$season <- "" # add season variable

# define seasons
#winter <- (rainfall$month == "Jun" | rainfall$month == "Jul" | rainfall$month == "Aug")
#spring <- (rainfall$month == "Sep" | rainfall$month == "Oct" | rainfall$month == "Nov")
#summer <- (rainfall$month == "Dec" | rainfall$month == "Jan" | rainfall$month == "Feb")
#autumn <- (rainfall$month == "Mar" | rainfall$month == "Apr" | rainfall$month == "May")

#rainfall$season[winter] <- "Winter"
#rainfall$season[spring] <- "Spring"
#rainfall$season[summer] <- "Summer"
#rainfall$season[earlysummer] <- "EarlySummer"
#rainfall$season[latesummer] <- "LateSummer"
#rainfall$season[autumn] <- "Autumn"

#rainfall$season <- factor(rainfall$season , levels=c('Summer', 'Autumn', 'Winter', 'Spring'))
```

>>>>

```{r VPD, echo=FALSE, message = FALSE, fig.width = 9, fig.height = 4}
group.colour <- c("19/20" = "#E69F00", "20/21" = "#009E73", "21/22" ="#D55E00")

(VPD.p <- ggplot(input.rearranged, aes(x = dayssinceJun1, y = VPD, group = GSYear)) +
  geom_line(aes(color = GSYear), size = 1)+
    scale_color_manual(values = group.colour) +
 # scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  xlab("Days since June 1st")+
   ylab("VPD (kPa")+
  theme_classic())+
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13),
          legend.text = element_text(size = 13),
          legend.title = element_text(size = 14))

VPD.p
#("VPD.tiff", units="in", width=10, height=6,  res=300)
#print(VPD.p)
#dev.off()

### ET

```{r VPD, echo=FALSE, message = FALSE, fig.width = 9, fig.height = 4}

(ET.p <- ggplot(input.rearranged, aes(x = dayssinceJun1, y = ET, group = GSYear)) +
  geom_line(aes(color = GSYear), size = 1)+
    scale_color_manual(values = group.colour) +
 # scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  xlab("Days since June 1st")+
   ylab("ET (mm day-1)")+
  theme_classic())+
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13),
          legend.text = element_text(size = 13),
          legend.title = element_text(size = 14))

ggplotly(ET.p)

#("ET.tiff", units="in", width=10, height=6,  res=300)
#print(ET.p)
#dev.off()

@@

```{r, echo=FALSE, message = FALSE, fig.width = 7, fig.height = 4}

@@

SWC.20
#tiff("SWC20.tiff", units="in", width=10, height=6,  res=300)
#print(SWC.20)
#dev.off()
```
